Efficient ancestry and mutation simulation with msprime 1.0

### 2021-12-01 paper.tex

The efficiency of coalescent simulations depends
crucially on the assumption of neutrality, and it is important
to note that there are many situations in which this will be a poor approximation
of biological reality~\citep{johri2021statistical}.
In particular, background selection has been shown to affect genomewide
sequence variation in a wide range of
species~\citep{charlesworth1993effect,charlesworth1995pattern,charlesworth2021effects}.
Thus care must be taken to ensure that the results of purely neutral simulations are
appropriate for the question and genomic partition under study.
A major strength of \msprime\ is that it can be used in conjunction
with forwards-time simulators, enabling the simulation of much
more realistic models than otherwise
possible~\citep{kelleher2018efficient,haller2018tree}.

>>>>

The efficiency of coalescent simulations depends
crucially on the assumption of neutrality, and it is important
to note that there are many situations in which this will be a poor approximation
of biological reality~\citep{johri2021statistical}.
In particular, background selection has been shown to affect genomewide
sequence variation in a wide range of
species~\citep{charlesworth1993effect,charlesworth1995pattern,charlesworth2021effects}.
Thus care must be taken to ensure that the results of purely neutral simulations are
appropriate for the question and genomic partition under study.
A major strength of \msprime, however, is that it can be used in conjunction
with forwards-time simulators, enabling the simulation of
more realistic models than otherwise
possible~\citep{kelleher2018efficient,haller2018tree}.
